% !TEX root = ../tex/thesis.tex

\setcounter{footnote}{0}


\chapter{Acknowledgements}


\vspace{10mm}

It's no secret that finishing the PhD was a difficult feat for me. I don't think I would have managed it without all the help and support I have received from colleagues, friends and family over the last four and a half years. Everybody I have interacted with has, in some way or form, shaped me and my journey through the PhD and I owe many of these people a special thank you.

First, I want to thank my supervisor. You provided me with the opportunity to move to Amsterdam and do a PhD in the first place. I learned a lot from working with you. Scientifically, professionally and personally. I will take this wisdom to my future endeavours even though I have left academia. It was also amazing to see you grow the group of exoplaneteers at API over the last few years. You have built a group of amazing scientists and I look forward to seeing the great science that each of them produces in the future.

Speaking of the group, I have discovered and learned so much from our meetings, group meetings, and conversations over the years. Thank you for being such an awesome team.

Thank you as well to all of my collaborators for reading my papers, providing insightful feedback and creating models for me. I learned a lot from my discussions with you and your contributions always made my papers better. An additional thanks to all of the conference/workshop/meeting/summer school organisers throughout the years. My interactions (social and professional) at all of these events greatly enhanced my PhD experience, I am lucky to have met and travelled with so many great people.

I would also like to express my gratitude to the API for being such a warm and accepting environment for me to be a researcher. From the first time I set foot in the Institute during my interview days, I felt immediately welcomed and included in the community. So a huge thanks to all of the staff, PhDs, postdocs, and students who play an important role in making the institute a special and unique place to do a PhD. I feel honoured to have been a part of such a great and forward-thinking community.

Before embarking on a PhD, I worked on several projects and was fortunate to have had a string of great scientists as supervisors. This was especially motivating as all of you happened to be women. You showed me that astrophysics is a place for everyone and I am deeply grateful to each of you. You gave me the support, guidance and encouragement I needed and ultimately inspired me to pursue a PhD. I couldn't believe my luck when one of you was already working at API when I started!

Speaking of strong females, I want to say a special thanks to the pillars (secretariat) of the API, for holding the place together, especially through all the chaos over the last few years. The Institute would not be the same without you, I think I speak for everyone when I say that you are the glue that brings everyone together and make API such a brilliant community to be a part of. You have always surpassed your official duties, and were always a friendly shoulder to cry on with a seemingly endless supply of sweeties. An additional thanks to the PhD evaluation committee, our director and my promotor for doing your best to take care of us and for making the PhD journey as smooth as possible.

Continuing with thanking the APIs, thanks to my two little hobbits, for all of the fun, beers, movie nights, travel adventures and for being great and supportive friends through all of the ups and downs of the PhD. Thanks to my API buddy for taking me under her wing at the beginning, for giving me the courage to be brave and for trying to teach me how to dance. Thanks to the API noobs and bake-off partners in crime for all of the delicious cake, dinners, risotto lessons and python help. Thanks to the API-in law who designed my wonderful thesis cover and to the one who always had Tea. Thanks to the avengers and quarantine bikers for the adventures, bike rides and for all of the fun socialising keeping me sane. Thanks to all of my office mates over the last 4 years for making the days at the office gezellig and productive. I will miss the random chats and the fancy coffee breaks. A special thanks to my two paranymphs: my little PhD brother and my fellow Brit abroad/wine buddy. I look forward to seeing both of your PhD theses soon.

A further thanks to all of the API athletes for all of the sporting adventures and fun over the years. I never thought a bunch of astronomers would run 160km through Germany in the middle of the night, but we did it! On the other hand, I never had any doubts that we would be able to party after running 160km. Thanks to my swimming partner, for the therapy and for pushing me to pick up biking and running as well. Thanks to my new swimming partner, for letting me convince him to join the triathlon club. And thanks to all the swimmers, gymmers and triathletes who have helped keep me fit and sane through the stressful moments.

Thanks to the Montelbaaners, for the Michelin star meals, the live music concerts, the pool parties, and the set of great memories. You guys were so welcoming, you introduced me to so many great people and I really felt like I had a second family in you all. Coming home to you guys turned the hard days into beautiful days. Additionally, a special thank you to all my homies in the West for the unconditional support, the extravagant brunches, the drunken evenings, the board games, the face squeezes, the Kubb in the park, and the walks when there was nothing else we could do. I look forward to more great adventures with you all.

Thanks to my physics pals and ex-housemates from Edinburgh, I can't wait to be reunited with you all again and to go on more ski trips in the future. A special thanks to the one who will always be up for spending a weekend in our pyjamas baking cookies no matter what extravagant location we happen to be meeting in. You guys made studying physics fun, which inspired me to pursue it further. I am extremely grateful for all the support and good times that we had over the years.

From school classmates to teenage party buddies, to making a WhatsApp chat solely dedicated to pictures of cats for when we're sad, you know who you are. Your friendship means the world to me. I am extremely grateful for everything that you have done for me and all of the good times we have had throughout the years, there are too many to list. A special thanks to your direct contribution to this thesis by kindly giving me feedback on my writing, I know it must have taken you a lot of time to read and understand my rambles. You are an amazing friend and I am honoured to be able to call you that, thank you for everything.

To the one to whom I almost got engaged. I am eternally grateful to you. You are always there when I need you and you have provided me with so much support and help ever since I knew you, especially with the writing! We have shared so many hilarious moments and I am extremely thankful for your friendship. Less than infinity.

To the guy who fixed my internet. Thank you for all of the support you gave me, for teaching me to trust myself, helping me grow, become a stronger person and dampening the tidal waves of the PhD with your calm and gentle approach to life.

The final words go to my wonderful parents and brother. I probably wouldn't even have chosen to study physics if I didn't look up to my big brother the way that I did. You always encouraged me to ask questions, think critically and carefully and inspired me to aim high. I know we don't speak every day, but I take a lot of comfort in knowing that you are always there for me if I need it. You are an amazing big brother and I wouldn't be the person that I am without you. As for our parents, I can very literally say that I wouldn't even be here without both of you. You have always supported me in every way possible no matter what happens. You let me follow my own path in life and have always been there without fail. Dad, you have taught me the value of being loyal, strong, standing up for myself yet always looking out for others. Mum, you are so kind, generous and patient with everyone in your life. I can talk to you about anything and everything, and you are always there to listen. You are all my rocks, none of this would have been possible without you, and I still have so much to learn from each of you.


\raggedleft
Claire

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../thesis_renzo"
%%% End:



%% For Ylva: first person I met in AMS
%% For Manos: SNe understanding at 3am in Chicheley Hall
%%
